UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-09-11 ms/main.tex
reorder supp figures
fix image
more image fixes

\begin{figure*}%
\centering
\begin{subfigure}{.5\columnwidth}
\includegraphics[width=\columnwidth]{images/UKBB_PC0_PC1_eth_crop.jpeg}%
\caption{}%
\label{fig:pc_ukbb}%
\end{subfigure}\hfill%
\begin{subfigure}{.5\columnwidth}
\includegraphics[width=\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_eth_labels.pdf}%
\caption{}%
\label{fig:umap_ukbb_pc10}%
\end{subfigure}%
\caption{\textbf{The UKBB coloured by self-reported ethnic background.} \textbf{(a)} The first two principal components, showing the usual triangle with vertices corresponding to African, Asian, and European ancestries, and intermediate values indicating admixture or lack of relationship to the vertex populations. \textbf{(b)} UMAP on the first 10 principal components. The cluster of White British and White Irish individuals is greatly expanded, with the Irish forming a distinct sub cluster mixed with the White British population. South Asian and East Asian individuals form their separate clusters, as do individuals of African or Caribbean backgrounds. Population clusters are connected by "trails" comprised of large proportions of individuals with mixed backgrounds.
BA, Black African; 
BC, Black Caribbean; 
BG, Bangladeshi; 
CHN, Chinese; 
IND, Indian;
PK, Pakistani;
WB, White British;
WI, White Irish;
WBC, White and Black Caribbean; 
WBA, White and Black African; 
WAA, White and Asian;
AAB, Any other Asian Background; 
ABB, Any other Black Background;
AWB, Any other White Background;
AMB, Any other Mixed Background;
OEG, Other ethnic group. 
}
\label{fig:fig_ukbb}
\end{figure*}

@@

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
    \includegraphics[width=0.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_ns_permuted_10nn_sd50000_base50000_201883118582.pdf}
    \includegraphics[width=.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_ew_permuted_10nn_sd50000_base50000_201883118582.pdf}
    \caption{}
    \label{fig:umap_ukbb_geo_osgb}
    \end{subfigure}
     \begin{subfigure}{\columnwidth}
         \includegraphics[width=0.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_2018714161841_Height_res_pct1_f.pdf}
    \includegraphics[width=.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_201871416519_leukocyte_count_pct5_f.pdf}
   \caption{}
    \label{fig:umap_height_female}
      \end{subfigure}
      \caption{\textbf{UMAP captures relationships between population structure, geography, and phenotype heterogeneity.} \textbf{(a)} Each individual is coloured by their geographical coordinates of residence. Coordinates follow the UKBB's OSGB1936 geographic grid system and represent distance from the Isles of Scilly, which lie southwest of Great Britain. The left image colours individuals by their north-south ("northing") coordinates, and the right image colours them by their east-west ("easting") coordinates. Adding more components creates finer clusters.  (figs~\ref{fig:supp_montage_ukbb_ns} and~\ref{fig:supp_montage_ukbb_ew}). Northing values were truncated between $100$km and $700$km, and easting values were truncated between $200$km and $600$km. \textbf{(b)} Females from the same projection coloured by age-adjusted difference from mean population height (left) and leukocyte counts (right). Individuals with missing data were excluded. To protect participant privacy, data in these images has been randomized as explained in the materials and methods section.}
\end{figure}

>>>>

\begin{figure*}%
\centering
\begin{subfigure}{.5\columnwidth}
\includegraphics[width=\columnwidth]{images/UKBB_PC0_PC1_eth_crop.jpeg}%
\caption{}%
\label{fig:pc_ukbb}%
\end{subfigure}\hfill%
\begin{subfigure}{.5\columnwidth}
\includegraphics[width=\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_eth_labels.jpeg}%
\caption{}%
\label{fig:umap_ukbb_pc10}%
\end{subfigure}%
\caption{\textbf{The UKBB coloured by self-reported ethnic background.} \textbf{(a)} The first two principal components, showing the usual triangle with vertices corresponding to African, Asian, and European ancestries, and intermediate values indicating admixture or lack of relationship to the vertex populations. \textbf{(b)} UMAP on the first 10 principal components. The cluster of White British and White Irish individuals is greatly expanded, with the Irish forming a distinct sub cluster mixed with the White British population. South Asian and East Asian individuals form their separate clusters, as do individuals of African or Caribbean backgrounds. Population clusters are connected by "trails" comprised of large proportions of individuals with mixed backgrounds.
BA, Black African; 
BC, Black Caribbean; 
BG, Bangladeshi; 
CHN, Chinese; 
IND, Indian;
PK, Pakistani;
WB, White British;
WI, White Irish;
WBC, White and Black Caribbean; 
WBA, White and Black African; 
WAA, White and Asian;
AAB, Any other Asian Background; 
ABB, Any other Black Background;
AWB, Any other White Background;
AMB, Any other Mixed Background;
OEG, Other ethnic group. 
}
\label{fig:fig_ukbb}
\end{figure*}

@@

\begin{figure}
    \centering
    \begin{subfigure}{\columnwidth}
    %\includegraphics[width=0.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_ns_permuted_10nn_sd50000_base50000_201883118582.pdf}
    %\includegraphics[width=.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_ew_permuted_10nn_sd50000_base50000_201883118582.pdf}
    \includegraphics[width=0.8\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_geo_permuted_10nn_sd50000_base50000_201883118582.pdf}
    \caption{}
    \label{fig:umap_ukbb_geo_osgb}
    \end{subfigure}
     \begin{subfigure}{\columnwidth}
         %\includegraphics[width=0.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_2018714161841_Height_res_pct1_f.pdf}
    %\includegraphics[width=.4\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_201871416519_leukocyte_count_pct5_f.pdf}
    \includegraphics[width=.8\columnwidth]{images/UKBB_UMAP_PC10_NN15_MD05_2018328174511_height_pct1_f_2018714161841_leukocyte_count_pct_5_f_201871416519.jpeg}
   \caption{}
    \label{fig:umap_height_female}
      \end{subfigure}
      \caption{\textbf{UMAP captures relationships between population structure, geography, and phenotype heterogeneity.} \textbf{(a)} Each individual is coloured by their geographical coordinates of residence. Coordinates follow the UKBB's OSGB1936 geographic grid system and represent distance from the Isles of Scilly, which lie southwest of Great Britain. The left image colours individuals by their north-south ("northing") coordinates, and the right image colours them by their east-west ("easting") coordinates. Adding more components creates finer clusters.  (figs~\ref{fig:supp_montage_ukbb_ns} and~\ref{fig:supp_montage_ukbb_ew}). Northing values were truncated between $100$km and $700$km, and easting values were truncated between $200$km and $600$km. \textbf{(b)} Females from the same projection coloured by age-adjusted difference from mean population height (left) and leukocyte counts (right). Individuals with missing data were excluded. To protect participant privacy, data in these images has been randomized as explained in the materials and methods section.}
\end{figure}
